A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}

### 2025-07-22 paper/main.tex
Swapped out one of the figures from PNG to PDF
Added a citation

On the other hand, in the regime $\tau \gg \sigma$, the leading edge of the EMG rises sharply (resembling the error function, $\erf$) and the trailing edge resembles the exponential kernel itself.
For this reason, pulse ToAs are typically mapped to the rising edge of highly scattered pulses, which closely approximates the centre of the original unscattered pulse.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.98\linewidth]{scattering_DM.png}
    \caption{Analysis of DM measurement errors if scattering is not properly taken into account. Panel (a) shows the errors measured for each defined type of ToA, normalised to the scale of the original pulse, $\sigma$. In panel (b), the predicted error in DM is shown if the ToA error (compared to a high-frequency ToA measurement) is erroneously attributed to dispersion. Panel (c) shows the rate of change of the ToA error with frequency, and panel (d) shows the error in DM measured if this rate of change (the `slope' of the pulse across the observed dynamic spectrum) is erroneously attributed to dispersion. In panels (c) and (d), the derived DM errors assume a pulse scale of $\sigma = 25\,$s and $\nu_s = 230\,$MHz, as estimated for \src{}. In all panels, the blue curves indicate \emph{negative} ToA errors (i.e. the measured ToAs are earlier than the pulse's unscattered mean, $\mu$), and the red curves indicate positive quantities.}
    \label{fig:scattering_DM}
\end{figure*}

>>>>

On the other hand, in the regime $\tau \gg \sigma$, the leading edge of the EMG rises sharply (resembling the error function, $\erf$) and the trailing edge resembles the exponential kernel itself.
For this reason, pulse ToAs are typically mapped to the rising edge of highly scattered pulses, which closely approximates the centre of the original unscattered pulse \citep[][and references therein]{2025arXiv250614519J}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.98\linewidth]{scattering_DM.pdf}
    \caption{Analysis of DM measurement errors if scattering is not properly taken into account. Panel (a) shows the errors measured for each defined type of ToA, normalised to the scale of the original pulse, $\sigma$. In panel (b), the predicted error in DM is shown if the ToA error (compared to a high-frequency ToA measurement) is erroneously attributed to dispersion. Panel (c) shows the rate of change of the ToA error with frequency, and panel (d) shows the error in DM measured if this rate of change (the `slope' of the pulse across the observed dynamic spectrum) is erroneously attributed to dispersion. In panels (c) and (d), the derived DM errors assume a pulse scale of $\sigma = 25\,$s and $\nu_s = 230\,$MHz, as estimated for \src{}. In all panels, the blue curves indicate \emph{negative} ToA errors (i.e. the measured ToAs are earlier than the pulse's unscattered mean, $\mu$), and the red curves indicate positive quantities.}
    \label{fig:scattering_DM}
\end{figure*}
